\tool

### 2018-02-12 paper/paper.tex

\documentclass[conference]{IEEEtran}
\usepackage{pdftexcmds}
\usepackage[pdftex]{graphicx}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{balance}
\usepackage{amssymb, marvosym}
\usepackage{threeparttable}
\usepackage[bookmarks=false]{hyperref}
\usepackage{url}
\PassOptionsToPackage{hyphens}{url}
\hypersetup{colorlinks=true,breaklinks=true}
\usetikzlibrary{patterns,shapes,arrows}
\newcommand\tab[1][.5cm]{\hspace*{#1}}
\hyphenation{op-tical net-works semi-conduc-tor}
\raggedbottom
\newcommand{\tool}{tool-recommender-bot}
\newcommand{\pseudosection}[1]{\vspace{2mm} \noindent {\bf #1}}
\newcommand{\pseudosubsection}[1]{\vspace{2mm} {\it #1}}

@@

\subsection{Design}
Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}. Many existing help systems simulate user-to-user recommendations to increase awareness of application tools and features.

@@

\pseudosection{Receptiveness}

@@

\pseudosubsection{1. Desire}

@@

\pseudosubsection{2. Familiarity}

@@

\subsection{Implementation}

@@

\pseudosubsection{1. Continuous Integration}

@@

\pseudosubsection{2. Fix Identification}

@@

\pseudosubsection{3. Fix Localizaton}

@@

\pseudosubsection{4. Code Review}

@@

We used real-world open source software applications from GitHub to evaluate \tool. To choose projects for our study from the millions of GitHub repositories, we selected projects that met the following criteria:

\begin{itemize}
\item primariy written in Java,
\item ranked as a 1000 forked repositoy for a month in the last 10 years,
\item builds with Maven, and
\item do not already utilize \textsc{Error Prone}.
\end{itemize}

\textsc{Error Prone} only analyzes Java code, so our evaluation was limited to Java projects. We chose the most forked repositories to sample the most popular GitHub projects in terms of developer activity. Additionally, GitHub suggests forking a repository as a best practice for contributing and making pull requests to projects\footnote{https://guides.github.com/activities/forking/}. Maven is a build automation and dependency management system for Java projects. \tool~requires Maven to automatically modify \textit{pom.xml} files by adding the \textsc{Error Prone} plug-in and running the static analysis tool. Using a GitHub search API with the above constraints, we identified 2003 projects to use for our evaluation.\footnote{\url{https://docs.google.com/spreadsheets/d/1MRmVPiUeDlYMa0UODzMmFbGeYBbahzdeEv1YSgqC1oo/edit?usp=sharing}}

@@

\pseudosection{RQ1}

@@

\pseudosection{RQ2}

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{pdftexcmds}
\usepackage[pdftex]{graphicx}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{balance}
\usepackage{amssymb, marvosym}
\usepackage{threeparttable}
\usepackage[bookmarks=false]{hyperref}
\usepackage{url}
\PassOptionsToPackage{hyphens}{url}
\hypersetup{colorlinks=true,breaklinks=true}
\usetikzlibrary{patterns,shapes,arrows}
\newcommand\tab[1][.5cm]{\hspace*{#1}}
\hyphenation{op-tical net-works semi-conduc-tor}
\raggedbottom
\newcommand{\tool}{tool-recommender-bot}
\newcommand{\pseudosection}[1]{\vspace{2mm} \noindent {\bf #1}}
\newcommand{\pseudosubsection}[1]{\vspace{2mm} \noindent{\it #1}}

@@

\pseudosection{Peer Interactions}
Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}. Many existing help systems simulate user-to-user recommendations to increase awareness of application tools and features.

@@

\pseudosubsection{Receptiveness}

@@

\subsubsection{Desire}

@@

\subsubsection{Familiarity}

@@

\pseudosection{Software Engineering}

@@

\pseudosubsection{Continuous Integration}

@@

\pseudosubsection{Fix Identification}

@@

\pseudosubsection{Fix Localizaton}

@@

\pseudosubsection{Code Review}

@@

We used real-world open source software applications to evaluate \tool. To choose study projects from the millions of GitHub repositories, we selected projects that met the following criteria:

\begin{itemize}
\item primariy written in Java,
\item ranked a top 1000 monthly forked repositoy in the last 10 years,
\item build using Maven, and
\item do not already utilize \textsc{Error Prone}.
\end{itemize}

We chose the most forked repositories to sample the most popular GitHub projects in terms of developer activity. Additionally, GitHub suggests forking repositories as a best practice for making contributions and pull requests to projects\footnote{https://guides.github.com/activities/forking/}. \textsc{Error Prone} only analyzes Java code, so this evaluation was limited to Java projects.  Maven is a build automation and dependency management system for Java projects. \tool~requires Maven to automatically modify \textit{pom.xml} files by adding the \textsc{Error Prone} plug-in and running the static analysis tool. Using a GitHub search API with the above constraints, we identified 2003 projects to use for our evaluation.\footnote{\url{https://docs.google.com/spreadsheets/d/1MRmVPiUeDlYMa0UODzMmFbGeYBbahzdeEv1YSgqC1oo/edit?usp=sharing}}

@@

\pseudosubsection{RQ1}

@@

\pseudosubsection{RQ2}
